Computational Luminance Constancy from Naturalistic Images

### 2018-10-23 Production/Revision1.tex
diff file

Here we used labeled images rendered from descriptions of virtual scenes. 
A similar approach has been used previously to study the perception of lightness and specularity \cite{toscani2013optimal,wiebel2015statistical,toscani2017lightness}. 
Our work adds to this approach by introducing color variation. 
There are many advantages to using rendered images \cite{Butler:ECCV:2012}. 
One advantage is that they allow us to work with large number of labeled images where object reflectance is precisely known at each pixel. A second advantage is that we can control the variation in distinct scene factors that might affect the difficulty of the estimation problem. This flexibility allows the study of individual scene factors as well as their combined effects. Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRF estimation. We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation of target object LRF. This type of question cannot be addressed using real images. The basic approach we use here can be extended to include parametric control over the amount of variation of different factors. For example, we could systematically vary the variances of the distribution over the weights that control the relative spectrum of the illumination.

@@

To increase the representativeness of our rendered images, we used datasets of natural surface reflectance spectra and natural daylight illumination spectra. Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved. For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses. Some of these datasets focused on the reflectance of objects (e.g. fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}). Another issue, not addressed by these datasets, is relative frequency of different surface reflectances in natural viewing. \citeNP{attewell2007distribution} performed a systematic survey, and report the distribution of an LRF-like quantity in natural scenes. Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.

>>>>

Here we used labeled images rendered from descriptions of virtual scenes. 
A similar approach has been used previously to study the perception of lightness and specularity \cite{toscani2013optimal,wiebel2015statistical,toscani2017lightness}. 
Our work adds to this approach by introducing color variation. 
There are many advantages to using rendered images \cite{Butler:ECCV:2012}. 
One advantage is that they allow us to work with large number of labeled images where object reflectance is precisely known at each pixel. A second advantage is that we can control the variation in distinct scene factors that might affect the difficulty of the estimation problem. This flexibility allows the impact of scene factors to be studied individually or in combination. Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRF estimation. We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation of target object LRF. This type of question cannot be addressed using real images. The basic approach we use here can be extended to include parametric control over the amount of variation of different factors. For example, we could systematically vary the variances of the distribution over the weights that control the relative spectrum of the illumination.

@@

To increase the representativeness of our rendered images, we used datasets of natural surface reflectance spectra and natural daylight illumination spectra. Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved. For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses. Some of these datasets focused on the reflectance of objects (e.g. fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}). Another issue, not addressed by these datasets, is relative frequency of different surface reflectances in natural viewing. \citeNP{attewell2007distribution} performed a systematic survey, and reported the distribution of an LRF-like quantity in natural scenes. Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.
